Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-30 paper.tex

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage{subcaption}

@@

\begin{figure}[htp!]
\centering
\subcaptionbox{All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$ \label{ccplot:a}}
{\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}}
\subcaptionbox{ Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$, compare to \cite{Takahashi2010} Fig. 14  \label{ccplot:b}}
{\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
\subcaptionbox{$D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. \label{ccplot:c}}
{\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}}
\caption{Correlation and comparisons between $F_{10.7}$ and $\rho_{eq}$}
\label{ccplot}
\end{figure}
\clearpage

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}

@@

\begin{figure}[htp!]
\centering
\subcaptionbox{\label{ccplot:a}}
{\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}}
\subcaptionbox{\label{ccplot:b}}
{\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
\caption{(a) All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$. (b) Correlation between $log(\rho_{eq})$ and $F_{10.7}$ at hour, day, and 27-day intervals; compare to \cite{Takahashi2010} Fig. 14}
\label{ccplot}
\end{figure}
\clearpage
